3D Magnetic modelling of ellipsoidal bodies

### 2017-02-17 manuscript/manuscript.tex
include the lambda matrix

For the particular case in which the susceptibility is isotropic,
the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
In this case, the magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde-remanence})
can be rewritten as follows:
\begin{equation}
\tilde{\mathbf{M}} = \left[ \begin{array}{ccc}
\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{11}} & 0 & 0 \\
0 & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{22}} & 0 \\
0 & 0 & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{33}}
\end{array} \right] \left( \chi \, \tilde{\mathbf{H}}_{0} +
\tilde{\mathbf{M}}_{R} \right) \: .
\label{eq:M-tilde-K-isotropic}
\end{equation}
This equation is in perfect agreement with those presented 
by \citet[Eqs. ~13--15]{guo2001}.
The first term, depending on the inducing field $\tilde{\mathbf{H}}_{0}$, 
represents the induced magnetization whereas the term depending on
$\tilde{\mathbf{M}}_{R}$ is the remanent magnetization.
Equation \ref{eq:M-tilde-K-isotropic} reveals that, as pointed out by \citet{maxwell1873},
the induced magnetization opposes the inducing field 
if it is parallel to an ellipsoid axis, 
independently of the ellipsoid type. Otherwise, the
magnetization is not necessarily parallel to
the inducing field.
If we additionally consider that $\chi << 1$, the magnetization
$\mathbf{M}$ (Eq. \ref{eq:M-KH}) defined in the main coordinate system
(Fig. \ref{fig:orientation-angles}a) can be approximated as follows:
\begin{equation}
\mathbf{M} \approx \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \: ,
\label{eq:M-approx}
\end{equation}
which is the classical equation describing the resultant
magnetization in applied geophysics \citep[p. ~89]{blakely1996}.
Notice that, in this particular case, the induced magnetization
is parallel to the inducing field $\mathbf{H}_{0}$ (Eq. \ref{eq:H0}),
whether it is parallel to an ellipsoid axis or not.
Usually, Eq. \ref{eq:M-approx}
is considered a good approximation for $\chi \leq 0.1$ SI.

>>>>

For the particular case in which the susceptibility is isotropic,
the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
In this case, the magnetization $\mathbf{M}$ (Eq. \ref{eq:M-KH}),
referred to the main coordinate system (Fig. \ref{fig:orientation-angles}a),
can be written as follows:
\begin{equation}
\mathbf{M} = \mathbf{\Lambda} \left( \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \right) \: ,
\label{eq:M-K-isotropic}
\end{equation}
where
\begin{equation}
\mathbf{\Lambda} = \mathbf{V}
\left[ \begin{array}{ccc}
\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{11}} &  &  \\
 & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{22}} &  \\
 &  & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{33}}
\end{array} \right] \mathbf{V}^{\top} \: .
\label{eq:Lambda}
\end{equation}
This equation is in perfect agreement with those presented 
by \citet[Eqs. ~13--15]{guo2001}.
The first term, depending on the inducing field $\mathbf{H}_{0}$
(Eq. \ref{eq:H0}), 
represents the induced magnetization whereas the term depending on
$\mathbf{M}_{R}$ is the remanent magnetization.
Equation \ref{eq:M-K-isotropic} reveals that, as pointed out by
many authors
\citep[e.g.,][]{maxwell1873, dubois1896, stoner1945, clark1986, sttraton2007},
the induced magnetization opposes the inducing field 
if it is parallel to an ellipsoid axis, 
independently of the ellipsoid type. Otherwise, the
magnetization is not necessarily parallel to
the inducing field.
If we additionally consider that $\chi << 1$, the matrix 
$\mathbf{\Lambda}$ (Eqs. \ref{eq:M-K-isotropic} and \ref{eq:Lambda})
approaches to the identity and the magnetization
$\mathbf{M}$ (Eqs. \ref{eq:M-KH} and \ref{eq:M-K-isotropic})
can be approximated as follows:
\begin{equation}
\mathbf{M} \approx \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \: ,
\label{eq:M-approx}
\end{equation}
which is the classical equation describing the resultant
magnetization in applied geophysics \citep[p. ~89]{blakely1996}.
Notice that, in this particular case, the induced magnetization
is parallel to the inducing field $\mathbf{H}_{0}$ (Eq. \ref{eq:H0}),
whether it is parallel to an ellipsoid axis or not.
Usually, Eq. \ref{eq:M-approx}
is considered a good approximation for $\chi \leq 0.1$ SI.
